\subsection{Stefan Majoor}
\begin{itemize}
 \item Abstract, Sections~\ref{sec:splitsolve} (SplitSolve), \ref{sec:rand} (Randomized Algorithm) and \ref{sec:comparison} (Comparison) of the report.
 \item Implementation of the randomized algorithm
 \item Implementation of the randomized density algorithm
 \item Implementation of the reductions rules used in iterative compression
 \item Implementation of the split solver
 \item First implementation of Simple Disjoint Algorithm
 \item Optimization of kernelization
\end{itemize}

\subsection{Huib Donkers}
\begin{itemize}
 \item Section~\ref{sec:itcomp} (Iterative compression) and Appendix~\ref{app:itcomp} (Experimental results Iterative Compression) of the report.
 \item Implementation of and improvements to the iterative compression algorithm
\end{itemize}

\subsection{Henk Alkema}
\begin{itemize}
 \item Subsection~\ref{sec:treewidth1} (Making tree decompositions) and subsection~\ref{sec:treewidth3} (Comparing found treewidths and FVS sizes) of the report.
 \item Implementation of and improvements to the tree decomposition creating algorithm.
 \item Subsection
\end{itemize}

\subsection{Xi Junquan}
\begin{itemize}
 \item Subsection~\ref{sec:dynamic program} (Dynamic programming based on given nice path decomposition) of the report.
 \item Implementation of and improvements to the dynamic programming for deciding whehter solution exists.
\end{itemize}

\subsection{Leo van Gansewinkel}
\begin{itemize}
 \item Fully refactored implementation of kernelization and approximation algorithm.
 \item Kernelization and format corrections to interactions with the input reader and input reader itself.
 \item Documentation on advanced kernelization.
\end{itemize}

\subsection{Christopher Ankomah}
\begin{itemize}
 \item Original implementation of the simple kernelization.
 \item Original implementation of the approximation algorithm. (DetermineFVS)
 \item Documentation on the simple kernelization and the approximation algorithm.
\end{itemize}

